|

### 2023-05-14 paper/04-results.Rmd
more results: players on the same team

In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the mean varying intercept for the top ten pass rushers for each position along with 95% confidence intervals. 
We observe similar rankings based on the random intercepts in comparison to the average STRAIN results in Tables \ref{tab:edge} and \ref{tab:interior}, with Myles Garrett (DE), Aaron Donald (DT), Vita Vea (NT), and T.J. Watt (OLB) as the top pass rusher for their respective position. 
We observe different levels of variability across these top players, with the only a subset of players with intervals strictly above zero. This is not necessarily surprising given the limited sample of data. Additionally, we are ignoring correlated performance between pass rushers on the same team, e.g., INSERT TWO PLAYERS ON SAME TEAM, but leave exploration of this for future work.

>>>>

In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the mean varying intercept for the top ten pass rushers for each position along with 95% confidence intervals. 
We observe similar rankings based on the random intercepts in comparison to the average STRAIN results in Tables \ref{tab:edge} and \ref{tab:interior}, with Myles Garrett (DE), Aaron Donald (DT), Vita Vea (NT), and T.J. Watt (OLB) as the top pass rusher for their respective position. 
We observe different levels of variability across these top players, with the only a subset of players with intervals strictly above zero. This is not necessarily surprising given the limited sample of data. Additionally, we are ignoring correlated performance between pass rushers on the same team.
For instance, the top two defensive ends, Myles Garrett and Takkarist McKinley (see the top panel of Figure \ref{fig:fig_rankings_boot}), are teammates on the Cleveland Browns.
McKinley is a surprising name in our list and we suspect that his high rank is mostly due to playing on the same defensive unit with Garrett, who is well-known as an elite pass rusher.
We leave the exploration of adjusting for teammates for future work.
